Identifiers for Iterative Forecasting

### 2021-03-09 paper/paper.Rmd

```{r}
query_sources("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

## Code formatting

Don't use markdown, instead use the more precise latex commands:

* \proglang{Java}
* \pkg{plyr}
* \code{print("abc")}

# R code

Can be inserted in regular R markdown blocks.

```{r}
x <- 1:10
x
```

>>>>

```{r results="hide"}
df <- query_sources("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
df
```

```{r echo=FALSE}
kableExtra::kable(df, "latex")
```

@@
